\chapter{Conclusion}

\section{Conclusion}

Drug discovery is an expensive and long-term business. It takes about US\$1.8 billion over 13.5 years to develop a new drug \citep{716-2010}. Drug discovery via merely biological and chemical means are both cost-inefficient and time-inefficient. Therefore we aim to develop a computational framework for structure-based drug discovery with GPU acceleration, simulating the early phases of modern drug discovery process in order to save money and time.

So far, we have developed three tools for this simulation purpose. The first tool, CUDAagrep, is used for fast approximate matching of DNA, which in essence directs the synthesis of proteins according to the central dogma. CUDAagrep facilitates the searching for viral DNA patterns producing viral proteins, which are probably drug targets. Compared with an OpenMP counterpart, CUDAagrep obtains a speedup of 33x to 83x, reducing querying time from the magnitude of dozens of seconds down to milliseconds. CUDAagrep requires no indexing at all and thus can be applied in real time. Its high sensitivity is guaranteed by strictly scanning through the entire genome. We have also developed an AJAX MVC website and an email crawler for real time online searching.

The second tool, idock, is used for fast predictions of both binding conformations of small compounds against given proteins and their binding affinities. idock can shortlist a few promising compounds out of millions for further clinical investigations. It is capable of screening 1.3 drug-like ligands per CPU minute on average, making it a competitive tool. Compared with Vina, idock achieved a speedup of 2.5x to 4.8x in terms of CPU time and a speedup of 6.3x to 10.4x in terms of elapsed time. We have also utilized idock to identify compounds for potential replacement of TDF, trying to retaining the efficacy and meanwhile minimizing the toxicity.

The third tool, SmartGrow, is used for computational synthesis of potent ligands. SmartGrow helps to explore a much larger chemical space for novel drugs. It inherits the mutation and crossover operators from AutoGrow, and invents two new genetic operators, namely split and merging, significantly enriching ligand diversity. The split operator ensures that ligands will not grow excessively large. The merging operator is basically a reversed operator of split and aims to accelerate ligand growing. SmartGrow implements Lipinski's \textit{Rule of Five} \citep{168-2004} to ensure drug likeness. The program design is so flexible that it reserves room for adaptation to new chemical constraints. Its robust parser correctly processes two-letter chemical elements, and meanwhile adds additional support for phosphorus. SmartGrow displays comparable performance in terms of predicted free energy but outperforms AutoGrow by 30\% in terms of execution time. Ligands generated by SmartGrow never exceed 500 Da so that they can be absorbed by human body. 

We have used our three new tools together with some other existing tools to discover potential new drugs for the treatments of acquired immune deficiency syndrome (AIDS) and Alzheimer's disease (AD). Several promising ligands have been computationally identified and synthesized for further clinical investigations.

\section{Future Work}

A comprehensive computational framework for drug discovery should incorporate capabilities of binding site identification, molecular docking, virtual screening, ligand synthesis, drug properties prediction, interactive visualization, and so on. The development of our three new tools is just the start. There is still a long way to go to fully implement all the capabilities.

For structure-based virtual screening, the most time consuming part is docking. Hence we plan to port idock to GPU, hoping to gain further speedup. This idea is feasible because there are GPU implementations of some other docking programs \citep{723-2009,652-2010,779-2011}, and we also have expertise in GPU programming.

For computational synthesis of potent ligands, even though SmartGrow implements Lipinski's \textit{Rule of Five}, it neglects selectivity, ADMET properties and other drug-like properties, possibly resulting in a high false positive rate. We plan to integrate SmartGrow and ADMET prediction methods into idock to gain speedup and compose a uniform interface.

For practical uses of our tools, we also plan to build a web server based on HTML5 technology to provide online drug discovery functionalities so that potential users, especially biologists and chemists, can easily utilize our tools without tedious software installation and configuration \citep{677-2011}.

\chapterend
