Drug discovery is an expensive and long-term business. It takes US\$1.8 billion over 13.5 years to develop a new drug. Therefore, we aim to develop a computational framework for drug discovery, simulating the early phases of modern drug discovery process in order to save money and time.

Protein-ligand docking is a key computational method in the design of starting points for the drug discovery process. We have developed idock, inheriting from AutoDock Vina the accurate scoring function and the efficient optimization algorithm, and significantly improving the fundamental implementation and numerical model for even faster execution. idock achieves a speedup of 3.3 in terms of CPU time and a speedup of 7.5 in terms of elapsed time on average.

<<<<<<< HEAD
We are motivated by the desire to automate large-scale docking using our popular docking engine idock and thus have developed a publicly-accessible web platform called istar. Without tedious software installation, users can submit jobs using our website. Our istar website supports 1) filtering ligands by desired molecular properties and previewing the number of ligands to dock, 2) monitoring job progress in real time, and 3) visualizing ligand conformations and outputting free energy and ligand efficiency predicted by idock, binding affinity predicted by RF-Score, putative hydrogen bonds, and supplier information for easy purchase, three useful features commonly lacked on other online docking platforms like DOCK Blaster or iScreen. We have collected 17,224,424 ligands from the All Clean subset of the ZINC database, and revamped our docking engine idock to version 2.0, further improving docking speed and accuracy, and integrating RF-Score as an alternative rescoring function.
=======
The first tool, idock, is used for fast protein-ligand docking. It predicts both binding conformations of ligands against given proteins and their binding affinities. Compared with AutoDock Vina, idock obtains a speedup of 6.3x to 10.4x, achieving a screening performance of 1.3 drug-like ligands per CPU minute.
>>>>>>> d14c83fb7fc187f2813e43ef8d6574c7a7dc713e

We have developed iview, an easy-to-use interactive WebGL visualizer of protein-ligand complex. It exploits hardware acceleration rather than software rendering. It features three special effects in virtual reality settings, namely anaglyph, parallax barrier and oculus rift, resulting in visually appealing identification of intermolecular interactions. It supports four surface representations including Van der Waals surface, solvent excluded surface, solvent accessible surface and molecular surface. Moreover, based on the feature-rich version of iview, we have also developed a neat and tailor-made version specifically for our istar web platform for protein-ligand docking purpose. This demonstrates the excellent portability of iview.

<<<<<<< HEAD
We have developed igrow, an de novo ligand design method. It synthesizes ligands from scratch by incorporating fragments. Compared with AutoGrow, ligands generated by igrow retain 100 Da lower molecular weights and 10\% lower free energies on average. In addition, igrow runs 30\% faster.

We have used our tools to discover potential new drugs for the treatments of influenza A and CCRK-related cancers. Several promising ligands have been computationally identified and syntehsized for further clinical investigations.
=======
We have used our three new tools together with some other existing tools to discover potential new drugs for the treatments of acquired immune deficiency syndrome (AIDS) and Alzheimer's disease (AD). Several promising ligands have been computationally identified and syntehsized for further clinical investigations.

We aim to develop a comprehensive and uniform framework incorporating capabilities of binding site identification, molecular docking, virtual screening, ligand synthesis, and interactive visualization. Eventually and most importantly, we should utilize this framework to discover new drugs in order to save millions of human lives.
>>>>>>> d14c83fb7fc187f2813e43ef8d6574c7a7dc713e
