\documentclass[12pt,conference,compsocconf]{../IEEEtran}
\usepackage{xltxtra}
%\usepackage{subfig}
%\usepackage{booktabs}
\usepackage{flushend}
\usepackage[numbers,sort&compress]{natbib}
\setmainfont{Times New Roman}

\begin{document}

\title{Chemical-Genetic Profiling and Its Applications}
\author
{
\IEEEauthorblockN
{
Hongjian Li
\IEEEauthorblockA
{
Department of Computer Science and Engineering\\
Chinese University of Hong Kong\\
hiji@cse.cuhk.edu.hk
}
}
}
\maketitle

\begin{abstract}

Chemical-genetic profiling of bioactive compounds has been repeatedly proved to be a powerful tool for identifying novel drugs, drug targets, and mode of actions. In the past decade, research mainly concentrated on applying chemical-genetic profiling to the yeast genome, but seldom investigated into higher organisms like mammals, or higher level of practical applications like drug synergy. This survey briefly reviews the popular experimental techniques and computational methods for constructing and analyzing chemical-genetic profiles and discusses their pros and cons. In the foreseeable future, as both the number of bioactive compounds and the number of sequenced genes increase, more and more chemical-genetic profiles will emerge. How to establish an universal database to accommodate diverse output from various research groups, and how to correctly and properly utilize such ressources for better drug discovery will become challenging issues.

\end{abstract}

\begin{IEEEkeywords}

Chemical-Genetic Profiling, Drug-Target Pathway, Mode-of-Action

\end{IEEEkeywords}

\section{Introduction}

Where the problem comes from?
Why it is important?

\section{Problem Definition}



\section{Existing Methods}

\citep{1078}
\citep{1079}
\citep{1080}
\citep{1103} tutorial
\citep{1081} is state-of-the-art review.
\citep{1082} is state-of-the-art review.

Comparison
Have your own evaluation
Use others results and give reasons

\section{Discussion}

Summary on current works
  Avoid overlapping with existing reviews

\section{Prospectives}

What will be done in the future?
  Consequences of current breakthroughs
  Bottleneck in the whole picture

\bibliographystyle{unsrtnat}
\bibliography{../refworks}

\end{document}
