I believe I would never have completed this thesis and gotten this far without the years of generous support of my supervisors, Prof. Kwong-Sak Leung and Prof. Man-Hon Wong, and I am sure that a simple thank you will never be enough to convey my gratitude for their criticisms and praises along the way. They provided gracious and vital help and a great deal of crucial feedback and substance in writing the thesis. They treated me with considerable respect and understanding and made me feel like a worthy researcher.

I feel extremely lucky and humbled to have had the opportunity to learn from such an impressive and supportive research group. The group members, Prof. Kwong-Sak Leung, Prof. Man-Hon Wong, Prof. Kin-Hong Lee, Prof. Kevin Yuk-Lap Yip, Prof. Stephen Kwok-Wing Tsui, Prof. Terrence Chi-Kong Lau, Prof. Mary Miu-Yee Waye, Benjamin Ching-Man Tse, Bing Ni, Cyrus Tak-Ming Chan, Shaoke Lou, Ricky Ka-Chun Wong, David Chi-Fai Lam, Peter Leung-Yau Lo, Jimmy Chun-Ting Yip, Kent Kin-Cheung Ling, Ka-Cheong Lam, Ethan Yizhen Zeng, and Xihao Hu, have inspired me in their own way to love and pursue my academic desires. They have all taught me to value and enjoy my education by modeling excellence in their teaching, scholarship, and innovation.

I would also like to thank my father Qiteng Li who have made incredible and selfless sacrifices for me over years that I might someday have this privilege. 

Last but not least, this thesis is dedicated in love and gratitude to my beloved girlfriend Shuyi Zhu, whose sacrifices, which were realized by our loss of precious time together, were for me the most painful and humbling of all. Thank you so much for all your encouragement, inspiration and patience. Thank you for being so proud of me and for believing in me for so long. Thank you for calling on and sharing with me your every little piece of matter in daily life, for listening to my endless complaints and annoyances, for going traveling together with me hand in hand, for buying warm clothes for me when the weather unconciously turned cold, for cooking my favorite fried-and-baked fish when I was at home, for leading me to hospitals when I felt sick from time to time, and for always being there for me with a shoulder to cry on. You truly are an honest and kind-hearted young lady. You make me happy when I'm around you. I have been so lucky that you appeared in my life. I would not be where I am today if it wasn't for you. I never wanted to have anything in my life that I couldn't stand losing. It is not because you are beautiful and smart and perfect. It is because I don't feel alone any more. There's no easy way since it gets harder each day. I can't be too late to say that I love you.
