I believe I would never have completed this thesis and gotten this far without five years of generous support of my supervisors, Prof. Kwong-Sak Leung and Prof. Man-Hon Wong. They treated me with considerable respect and understanding, and made me feel like a worthy researcher. I am sure that a simple thank you will never be enough to convey my gratitude for their praises and criticisms along the way.

I feel extremely lucky and humbled to have had the opportunity to learn from an impressive and supportive research group led by Prof. Kwong-Sak Leung, Prof. Man-Hon Wong, Prof. Kin-Hong Lee and Prof. Kevin Yuk-Lap Yip. I would extend my sincere thanks to my fellow postgraduate students, Cyrus Tak-Ming Chan, Shaoke Lou, David Chi-Fai Lam, Peter Leung-Yau Lo, Xihao Hu and Ho Yin Szeto. They have inspired me in their own way to pursue my academic desires, and taught me to enjoy my education by modeling excellence in their teaching, scholarship and innovation. I would also like to express my heartfelt gratitude to my undergraduate students, Chun Ho Chan and Hei Lun Cheung, who implemented useful software.

It has been a great pleasure to collaborate with excellent scholars in my research field. Dr. Pedro J. Ballester provided me encouraging and illuminating instructions in doing novel research and writing academic manuscripts. Takanori Nakane helped me get acquainted with the visualization domain and was always willing to share with me his source code. Prof. Marie Chia-Mi Lin and Xilan Shi conducted biological experiments and augmented my pure computational research.

I am particularly indebted to my father Qiteng Li, who have made incredible and selfless sacrifices for me over years that I might someday have this privilege. He always listened to me and helped me work out many little troubles in my daily life.
