\chapter{Publications}

\section{Journal publications}

1) \textbf{Hongjian Li}, Kwong-Sak Leung, Pedro J. Ballester and Man-Hon Wong. istar: A Web Platform for Large-Scale Protein-Ligand Docking. \textit{PLoS ONE}, 9(1):e85678, 2014. DOI: 10.1371/journal.pone.0085678

2) \textbf{Hongjian Li}, Kwong-Sak Leung, Takanori Nakane and Man-Hon Wong. iview: an interactive WebGL visualizer for protein-ligand complex. \textit{BMC Bioinformatics}, 15(1):56, 2014. DOI: 10.1186/1471-2105-15-56

3) \textbf{Hongjian Li}, Kwong-Sak Leung, Man-Hon Wong and Pedro J. Ballester. Substituting random forest for multiple linear regression improves binding affinity prediction of scoring functions: Cyscore as a case study. \textit{BMC Bioinformatics}, 15(1):291, 2014. DOI: 10.1186/1471-2105-15-291

\section{Conference publications}

1) \textbf{Hongjian Li}, Kwong-Sak Leung, and Man-Hon Wong. idock: A Multithreaded Virtual Screening Tool for Flexible Ligand Docking. In \textit{Proceedings of the 2012 IEEE Symposium on Computational Intelligence in Bioinformatics and Computational Biology (CIBCB)}, San Diego, US, 9-12 May 2012. DOI: 10.1109/CIBCB.2012.6217214

2) \textbf{Hongjian Li}, Kwong-Sak Leung, Man-Hon Wong and Pedro J. Ballester. The importance of the regression model in the prediction of intermolecular binding using AutoDock Vina. In \textit{Proceedings of the 11th International Meeting on Computational Intelligence Methods for Bioinformatics and Biostatistics (CIBB)}, Cambridge, UK, 26-28 June 2014.

3) \textbf{Hongjian Li}, Kwong-Sak Leung, Man-Hon Wong and Pedro J. Ballester. The impact of docked pose generation error on the accuracy of machine-learning scoring functions. In \textit{Proceedings of the 11th International Meeting on Computational Intelligence Methods for Bioinformatics and Biostatistics (CIBB)}, Cambridge, UK, 26-28 June 2014.

4) \textbf{Hongjian Li}, Kwong-Sak Leung, Chun Ho Chan, Hei Lun Cheung, and Man-Hon Wong. iSyn: De Novo Drug Design with Click Chemistry Support. In \textit{Proceedings of the 2014 Conference Companion on Genetic and Evolutionary Computation Conference (GECCO)}, Vancouver, Canada, 12-16 July 2014. DOI: 10.1145/2598394.2598398

5) \textbf{Hongjian Li}, Kwong-Sak Leung, Chun Ho Chan, Hei Lun Cheung, and Man-Hon Wong. iSyn: WebGL-based interactive de novo drug design. In \textit{Proceedings of the 18th International Conference on Information Visualisation (IV)}, Paris, France, 15-18 July 2014. DOI: 10.1109/IV.2014.10

\chapterend
